Let's play congestion control

### 2018-01-17 tex/neural_network.tex

\centering
\begin{tikzpicture}[every label/.append style={font=\tiny}, node distance=1.2cm, >=stealth',bend angle=45,auto]

@@

  \begin{scope}
    \node [input place] (s1) [label={[align=center]left: State (12)}] {};
    \node [place] (s2) [above right of=s1, label={[align=center]above: Linear}] {};

@@

    \node [output place] (s17) [right of=s13, label={[align=center]above: $V_\text{packets}$ (1)}] {};

  \path[->] (s13) edge node {} (s17);

    \node [place] (s15) [below of=s13, label={[align=center]above: Linear}] {};

  \path[->] (s12) edge node {} (s15);

    \node [output place] (s19) [right of=s15, label={[align=center]above: $V_\text{delay}$ (1)}] {};

  \path[->] (s15) edge node {} (s19);

    \node [place] (s16) [below of=s15, label={[align=center]above: Linear}] {};

@@

    \node [output place] (s20) [right of=s16, label={[align=center]above: $V_\text{sent}$ (1)}] {};

@@

    \node [place] (s14) [below of=s16, label={[align=center]above: Linear}] {};

  \path[->] (s12) edge node {} (s14);

    \node [output place] (s21) [right of=s14, label={[align=center]above: $V_\text{duration}$ (1)}] {};

  \path[->] (s14) edge node {} (s21);

@@

>>>>

\newcommand{\nodedistance}{1.2}
\newcommand{\neuralnetworkwidth}{32}

\pgfmathsetmacro{\shortside}{sqrt((\nodedistance * \nodedistance ) /2)}
\pgfmathsetmacro{\solutionx}{ \shortside }
\pgfmathsetmacro{\solutiony}{ - (3 * \shortside + 3 * \nodedistance ) }

\pgfmathsetmacro{\solutiondurationx}{ \shortside }
\pgfmathsetmacro{\solutiondurationy}{ - (2 * \shortside + 2 * \nodedistance ) }

\centering
\begin{tikzpicture}[every label/.append style={font=\tiny}, node distance=\nodedistance cm, >=stealth',bend angle=45,auto]

@@

  \begin{scope}
    \node [input place] (s1) [label={[align=center]left: State (15)}] {};
    \node [place] (s2) [above right of=s1, label={[align=center]above: Linear}] {};

@@

    \node [output place] (s17) [right of=s13, label={[align=center]above: $V_\text{received}$ (1)}] {};

  \path[->] (s13) edge node {} (s17);
%    
%    \node [place] (s15) [below of=s13, label={[align=center]above: Linear}] {};
%    
%  \path[->] (s12) edge node {} (s15);
%
%    \node [output place] (s19) [right of=s15, label={[align=center]above: $V_\text{delay}$ (1)}] {};

%  \path[->] (s15) edge node {} (s19);

    \node [place] (s16) [below of=s13, label={[align=center]below: Linear}] {};

@@

    \node [output place] (s20) [right of=s16, label={[align=center]below: $V_\text{sent}$ (1)}] {};

@@

    \node [place] (s40) at (\solutiondurationx cm,\solutiondurationy cm) [label={[align=center]below: Linear}] {};

  \path[->] (s1) edge node {} (s40);

    \node [lstm place] (s41) [right of=s40, label={[align=center]above: GRU (32)}] {};

  \path[->] (s40) edge node {} (s41);
  \path[->] (s41) edge [loop below] node {} (s41);

    \node [lstm place] (s42) [right of=s41, label={[align=center]above: GRU (32)}] {};

  \path[->] (s41) edge node {} (s42);
  \path[->] (s42) edge [loop below] node {} (s42);

    \node [place] (s43) [right of=s42, label={[align=center]above: Linear}] {};

  \path[->] (s42) edge node {} (s43);

    \node [output place] (s44) [right of=s43, label={[align=center]above: $V_\text{duration}$ (1)}] {};

  \path[->] (s43) edge node {} (s44);

@@

%    \node [place] (s30) at (\solutionx cm,\solutiony cm) [label={[align=center]below: Linear}] {};
%
%  \path[->] (s1) edge node {} (s30);   
%
%    \node [lstm place] (s31) [right of=s30, label={[align=center]above: GRU (\neuralnetworkwidth)}] {};
%    
%  \path[->] (s30) edge node {} (s31);
%  \path[->] (s31) edge [loop below] node {} (s31);
%
%    \node [lstm place] (s32) [right of=s31, label={[align=center]above: GRU (\neuralnetworkwidth)}] {};
%    
%  \path[->] (s31) edge node {} (s32);
%  \path[->] (s32) edge [loop below] node {} (s32);
%    
%    \node [place] (s33) [right of=s32, label={[align=center]above: Linear}] {};
%    
%  \path[->] (s32) edge node {} (s33);
%
%    \node [output place] (s34) [right of=s33, label={[align=center]above: $V_\text{byte}$ (1)}] {};
%    
%  \path[->] (s33) edge node {} (s34);
